Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-03-28 PAPER/main.tex
bold values in table for best optimality

\section{Comparison}
In order to provide a complete overview of the heuristics, sets of 100, 500, and 1000 items were used on strips of lengths 1500, 2500, and 5000. Item widths were randomly selected between 150 and 1000, and score widths between 1 and 70. This ensures that each item has two score lines.

>>>>

\section{Comparison}
In order to provide a complete overview of the heuristics, sets of 100, 500, and 1000 items were used on strips of lengths 1250, 2500, and 5000. Item widths were randomly selected between 150 and 1000, and score widths between 1 and 70. This ensures that each item has two score lines. Changing the strip lengths changes the average number of items per strip.

\begin{table}[!htb]
\centering
\caption{$n = 100$}
\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
	\noalign{\smallskip}
	& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
	\hline\noalign{\smallskip}
	$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
	\noalign{\smallskip}
	\hline 
	\noalign{\smallskip}
	0.0 & 0.119930 & 0.119930 & 0.119930 & 0.234780 & 0.234780 & 0.234780 & 0.464660 & 0.464660 & 0.464660 \\
	0.1 & 0.190373 & \textbf{0.209209} & 0.195007 & 0.368315 & \textbf{0.403484} & 0.372649 & 0.653776 & \textbf{0.662649} & 0.654527 \\
	0.2 & 0.241823 & \textbf{0.291742} & 0.252201 & 0.455307 & \textbf{0.537355} & 0.464804 & 0.740613 & \textbf{0.743163} & 0.74212 \\
	0.3 & 0.308598 & \textbf{0.423971} & 0.330489 & 0.552257 & \textbf{0.700541} & 0.573676 & 0.817858 & 0.801526 & \textbf{0.820929} \\
	0.4 & 0.387256 & \textbf{0.634770} & 0.435353 & 0.648313 & \textbf{0.860270} & 0.688716 & 0.874070 & 0.835449 & \textbf{0.878158} \\
	0.5 & 0.491093 & \textbf{0.900872} & 0.586398 & 0.747025 & \textbf{0.953757} & 0.806812 & 0.915534 & 0.854677 & \textbf{0.920727} \\
	0.6	& 0.612443 & \textbf{0.982422} & 0.753466 & 0.834971 & \textbf{0.962939} & 0.896095 & 0.939964 & 0.864190 & \textbf{0.945036} \\
	0.7 & 0.773879 & \textbf{0.986985} & 0.909705 & 0.916026 & \textbf{0.965898} & 0.959666 & 0.957970 & 0.873854 & \textbf{0.961036} \\
	0.8	& 0.904347 & \textbf{0.987407} & 0.980250 & 0.966750 & 0.967486 & \textbf{0.984634} & 0.964117 & 0.885786 & \textbf{0.965271} \\
	0.9	& 0.978801 & 0.984535 &	\textbf{0.991745} & 0.987382 & 0.967989 & \textbf{0.990479} & 0.968735 & 0.897915 & \textbf{0.968928} \\
	1.0 & \textbf{0.995493} & 0.988851 & \textbf{0.995493} & \textbf{0.992539} & 0.969239 & \textbf{0.992539} & \textbf{0.967834} & 0.904161 & \textbf{0.967834} \\
	\hline
\end{tabular}
\label{table:n100}
\end{table}

\begin{table}[!htb]
	\centering
	\caption{$n = 500$}
	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
		\noalign{\smallskip}
		& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
		\hline\noalign{\smallskip}
		$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
		\noalign{\smallskip}
		\hline
		\noalign{\smallskip}
		0.0 & 0.116078 & 0.116078 &	0.116078 & 0.231142 & 0.231142 & 0.231142 & 0.461296 & 0.461296 & 0.461296 \\
		0.1 & 0.191817 & \textbf{0.206796} & 0.193715 & 0.375914 & \textbf{0.403863} & 0.376151 & 0.65971 & \textbf{0.67634} & 0.659638 \\
		0.2	& 0.247985 & \textbf{0.289553} & 0.251505 & 0.471136 & \textbf{0.541779} & 0.471511 & 0.753568 & \textbf{0.757848} & 0.753592 \\
		0.3	& 0.321577 & \textbf{0.426852} & 0.329629 & 0.578598 & \textbf{0.717203} & 0.585497 & 0.836553 & 0.813063 & \textbf{0.837042} \\
		0.4	& 0.411209 & \textbf{0.660488} & 0.436567 & 0.686034 & \textbf{0.886587} & 0.709649 & 0.900865 & 0.846469 & \textbf{0.902393} \\
		0.5	& 0.526376 & \textbf{0.967058} & 0.597456 & 0.793717 & \textbf{0.968396} & 0.838188 & 0.946179 & 0.867053 & \textbf{0.950434} \\
		0.6	& 0.672678 & \textbf{0.987213} & 0.805681 & 0.890082 & \textbf{0.971239} & 0.935295 & 0.97161 & 0.881001 & \textbf{0.976682} \\
		0.7	& 0.839117 & \textbf{0.987909} & 0.959455 & 0.953589 & 0.973028 & \textbf{0.981477} & 0.983071 & 0.898796 & \textbf{0.986087} \\
		0.8	& 0.954183 & 0.987787 &	\textbf{0.991791} & 0.984277 & 0.97413 & \textbf{0.992152} & 0.987373 & 0.917181 & \textbf{0.988403} \\
		0.9	& 0.99056 &	0.988561 & \textbf{0.995444} & 0.992356 & 0.974811 & \textbf{0.993584} & 0.988397 & 0.931674 & \textbf{0.988545} \\
		1.0	& \textbf{0.99555} & 0.987811 & \textbf{0.99555} & \textbf{0.993626} & 0.974892 & \textbf{0.993626} & \textbf{0.988883} & 0.938649 & \textbf{0.988883} \\
		\hline
	\end{tabular}
	\label{table:n500}
\end{table}

\begin{table}[!htb]
	\centering
	\caption{$n = 1000$}
	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
		\noalign{\smallskip}
		& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
		\hline\noalign{\smallskip}
		$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
		\noalign{\smallskip}
		\hline
		\noalign{\smallskip}
		0.0	&0.115534&	0.115534&	0.115534&	0.230563&	0.230563&	0.230563&	0.460623&	0.460623&	0.460623 \\
		0.1	&0.193119&	\textbf{0.206222} &	0.194298&	0.379134&	\textbf{0.402463}&	0.378162&	0.6614&	\textbf{0.681008}&	0.661144 \\
		0.2	&0.251658&	\textbf{0.289114} &	0.253138&	0.478121&	\textbf{0.538655}&	0.475984&	0.758956&	\textbf{0.763423}&	0.758428 \\
		0.3	&0.328699&	\textbf{0.427652} &	0.332872&	0.590141&	\textbf{0.711773}&	0.593915&	\textbf{0.84551}&	0.818874&	0.845116 \\
		0.4	&0.420561&	\textbf{0.65769} &	0.44084&	0.701106&	\textbf{0.8834}&	0.722513&	0.909988&	0.854863&	\textbf{0.910882} \\
		0.5	&0.542993&	\textbf{0.976737} &	0.611842&	0.814597&	\textbf{0.970731}&	0.856799&	0.957862&	0.874602&	\textbf{0.961627} \\
		0.6	&0.703725&	\textbf{0.987923} &	0.839692&	0.911433&	\textbf{0.973308}&	0.95286&	0.980911&	0.889836&	\textbf{0.985533} \\
		0.7	&0.866696&	\textbf{0.98822} 	& 0.974979&	0.966382&	0.974971&	\textbf{0.987669}&	0.98836&	0.907816&	\textbf{0.990632} \\
		0.8	&0.968441&	0.988482& \textbf{0.993951} &	0.989124&	0.976005&	\textbf{0.993392}&	0.991248&	0.927659&	\textbf{0.991882} \\
		0.9	&0.99348&	0.988613& \textbf{0.995965} &	0.993528&	0.97652&	\textbf{0.994038}&	0.992179&	0.944748&	\textbf{0.992259} \\
		1.0	& \textbf{0.995915} & 0.988288&	\textbf{0.995915} &	\textbf{0.994067}&	0.976631&	\textbf{0.994067}&	\textbf{0.992197}&	0.948814&	\textbf{0.992197} \\
		\hline
	\end{tabular}
	\label{table:n1000}
\end{table}
